
\documentclass[10pt,a4paper]{article}
\usepackage[margin=1.65cm]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[scaled]{helvet}
\renewcommand\familydefault{\sfdefault}
\usepackage{xcolor,hyperref,enumitem,titlesec,tabularx}
\definecolor{navy}{HTML}{002244}\definecolor{blue}{HTML}{0071BC}\definecolor{muted}{HTML}{4B5563}
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=blue}
\titleformat{\section}{\large\bfseries\color{navy}}{}{0pt}{}[\titlerule]
\setlist[itemize]{leftmargin=*,itemsep=2pt,topsep=2pt}
\setlength{\parindent}{0pt}
\pagenumbering{arabic}
\begin{document}
{\Huge\bfseries\color{navy} Mesfin Genie}\hfill {\small Last updated July 2026}\\[3pt]
{\large Continuing Senior Lecturer in Health Economics}\\
Newcastle Business School, The University of Newcastle, Australia\\
\href{mailto:mesfin.genie@newcastle.edu.au}{mesfin.genie@newcastle.edu.au} \; | \; \href{https://mesfingenie.com}{mesfingenie.com} \; | \; \href{https://orcid.org/0000-0002-1744-4666}{ORCID} \; | \; \href{https://scholar.google.com/citations?user=v2SXM_kAAAAJ\&hl=en}{Google Scholar}
\section*{Profile}
Health economist and behavioural economist using stated-preference methods, discrete choice experiments, eye tracking, applied econometrics and decision-support tools to study healthcare decisions, public preferences and policy design.
\section*{Appointments}
\begin{itemize}
\item Continuing Senior Lecturer in Health Economics, Newcastle Business School, The University of Newcastle, Australia, 2026--present.
\item Lecturer in Health Economics, Newcastle Business School, The University of Newcastle, Australia, 2023--2025.
\item Previous research and teaching roles at Ca' Foscari University of Venice, University of Aberdeen, Auburn University and Duke University.
\end{itemize}
\section*{Education}
\begin{itemize}
\item PhD in Economics, Ca' Foscari University of Venice, Italy, 2019.
\item MSc in Health Economics and Management, University of Bologna, Italy, 2015.
\item MSc in Economics, Addis Ababa University, Ethiopia, 2010.
\item BA in Economics, Jimma University, Ethiopia, 2006.
\end{itemize}
\section*{Selected grants and funded work}
\begin{itemize}
\item MandEval: effectiveness and consequences of Australia's COVID-19 vaccine mandates, MRFF Early to Mid-Career Researchers, MRF2019107, 2023--2025. University of Newcastle component A\$808,440; verified multi-institution programme A\$4,754,183.37.
\item Upscaling FETP in India Business Case, World Bank Group, 2025, A\$416,000. Role: Lead, University of Newcastle project team.
\item ASHEcon/NIA support, 2019. Novartis Travel Grant, 2017. Royal Economic Society Conference Grant, 2017.
\end{itemize}
\section*{Teaching}
\begin{itemize}
\item ECON3011 Introduction to Health Economics and Finance.
\item ECON2112 Health Economics and Finance.
\item ECON3111 Behavioural Economics.
\end{itemize}
\section*{Research supervision}
Current and completed supervision includes PhD and MPhil projects in climate-change economics, crop drought resilience, gendered ageism, telehealth, health-system reform and vaccine mandates.
\section*{Selected publications}
\begin{itemize}
\item Fabio I. Martinenghi; Tushar P. Ojha; Anaïs Thomasson; Bianca Devsam; Sarah Drislane; Stavros Vasiliadis; Chiara Berardi; Aregawi Gebremariam; Arianna Dipalma; Teresa Gavaruzzi; Jeremy K. Ward; Francesco Paolucci; Margie Danchin; Mesfin Genie; Katie Attwell; Christopher C. Blyth. \textit{npj Vaccines}, 2026. ``An Open Repository of COVID-19 Vaccine Mandate Studies with a Worked Scoping Review of Quasi-experimental Evidence.'' \href{https://doi.org/10.1038/s41541-026-01454-4}{DOI: 10.1038/s41541-026-01454-4}
\item Mesfin Genie; Fabio I. Martinenghi; Francesco Paolucci; Jonathan Lake; Katie Attwell; Christopher C. Blyth; Margie Danchin; Teresa Gavaruzzi; Udo Evers. \textit{Australian and New Zealand Journal of Public Health}, 2026. ``Community First or My Body First? Moral Values and Vaccine Mandate Preferences.'' \href{https://doi.org/10.1016/j.anzjph.2026.100496}{DOI: 10.1016/j.anzjph.2026.100496}
\item Mesfin G. Genie; Allison W. Boyes; Francesco Paolucci. \textit{Health Policy}, 2026. ``Feeling Lonely? Preferences for Support Programmes to Reduce Loneliness among Older Adults in Australia: A Discrete Choice Experiment.'' \href{https://doi.org/10.1016/j.healthpol.2026.105587}{DOI: 10.1016/j.healthpol.2026.105587}
\item Mesfin G. Genie; Verity Watson; Michaël Schwarzinger; Stéphane Luchini. \textit{Social Science \& Medicine}, 2026. ``Fit for Purpose? Assessing the Robustness of Discrete Choice Experiment Designs in the Context of Evolving Health Technologies.'' \href{https://doi.org/10.1016/j.socscimed.2026.119463}{DOI: 10.1016/j.socscimed.2026.119463}
\item Mesfin G. Genie; Shelby D. Reed; Semra Ozdemir. \textit{Health Economics}, 2026. ``Guidance or Misdirection? Unpacking the Role of Feedback in Health Preference Assessments.'' \href{https://doi.org/10.1002/hec.70093}{DOI: 10.1002/hec.70093}
\item Raluca Elena Buia; Mesfin Genie; Cristina Elisa Orso; Giacomo Pasini. \textit{Empirical Economics}, 2026. ``Immigration and Preventive Care Utilization in Europe: Evidence from Retrospective Data.'' \href{https://doi.org/10.1007/s00181-026-02928-z}{DOI: 10.1007/s00181-026-02928-z}
\item Stefano Bruzzo-Gallardo; Josefa Henriquez; Mesfin G. Genie. \textit{Health Policy and Technology}, 2026. ``Jabs and Lockdowns: Public Preferences for Vaccination Programmes in Chile.'' \href{https://doi.org/10.1016/j.hlpt.2026.101196}{DOI: 10.1016/j.hlpt.2026.101196}
\item Aregawi G. Gebremariam; Mesfin G. Genie; Beidemaryam Wondwosen Admasu; D. Abegaz; J. G. Gatua; Surachat Ngorsuraches; Francesco Paolucci. \textit{Health Policy and Technology}, 2026. ``Jabs or Societal Restrictions? Public Preferences for Vaccination Programmes in South Africa.'' \href{https://doi.org/10.1016/j.hlpt.2026.101195}{DOI: 10.1016/j.hlpt.2026.101195}
\item Mesfin Genie; Fabio I. Martinenghi; Francesco Paolucci; Jonathan Lake; Katie Attwell; Christopher C. Blyth; Jessica Kaufman; Margie Danchin; Jeremy K. Ward; Teresa Gavaruzzi. \textit{Australian and New Zealand Journal of Public Health}, 2026. ``No Jab, No Access? Preferences for Vaccine Mandates in Europe and Australia.'' \href{https://doi.org/10.1016/j.anzjph.2026.100450}{DOI: 10.1016/j.anzjph.2026.100450}
\item Mesfin G. Genie; Surachat Ngorsuraches. \textit{Value in Health}, 2026. ``Priority for Self or Others? Incorporating Equity Considerations in a Preference-Based Health Value Assessment.'' \href{https://doi.org/10.1016/j.jval.2025.10.011}{DOI: 10.1016/j.jval.2025.10.011}
\item Ibrahim Alfayoumi; Mesfin G. Genie; Surachat Ngorsuraches. \textit{Health Policy and Technology}, 2026. ``Shots or Shutdowns? Public Preferences for COVID-19 Vaccines and Societal Restrictions in the US.'' \href{https://doi.org/10.1016/j.hlpt.2025.101152}{DOI: 10.1016/j.hlpt.2025.101152}
\item Arthur E. Attema; Marcello Antonini; Mesfin Genie; Aleksandra Torbica; Francesco Paolucci. \textit{The European Journal of Health Economics}, 2026. ``Time Preferences and COVID-19 Vaccination Uptake.'' \href{https://doi.org/10.1007/s10198-025-01801-7}{DOI: 10.1007/s10198-025-01801-7}
\item Yevgen Bogodistov; Mesfin Genie; Ayman Fouda. \textit{Health Policy and Technology}, 2026. ``Understanding Vaccine Acceptance through Construal-Level Theory of Psychological Distance: Evidence from Singapore and South Korea.'' \href{https://doi.org/10.1016/j.hlpt.2025.101148}{DOI: 10.1016/j.hlpt.2025.101148}
\item Chiara Berardi; Ayman Fouda; Mesfin Genie; Aleksandra Torbica. \textit{Health Policy and Technology}, 2026. ``Vaccination Policies and Hesitancy: Preferences, Trade-offs and Future Challenges.'' \href{https://doi.org/10.1016/j.hlpt.2026.101246}{DOI: 10.1016/j.hlpt.2026.101246}
\item Aregawi G. Gebremariam; Mesfin Genie; Huong Le; Annette K. Regan; Frank H. Beard; Kristine Macartney; Francesco Paolucci; Hannah C. Moore; Katie Attwell; Christopher C. Blyth. \textit{Vaccine}, 2026. ``Vaccine Uptake in the Context of Mandate Announcement and Removal: Evidence from Europe and North America.'' \href{https://doi.org/10.1016/j.vaccine.2026.128825}{DOI: 10.1016/j.vaccine.2026.128825}
\item Stefano Bruzzo-Gallardo; Mesfin Genie; R. Gallagher; Francesco Paolucci. \textit{Information Technologies in the Healthcare Industry}, 2025. ``Telehealth Evolution and Policy Response in Australia: Insights from the COVID-19 Pandemic.'' \href{https://doi.org/10.1016/B978-0-443-30168-1.00002-5}{DOI: 10.1016/B978-0-443-30168-1.00002-5}
\item Marcello Antonini; Mesfin G. Genie; Katie Attwell; Arthur E. Attema; Jeremy K. Ward; Alessia Melegaro; Aleksandra Torbica; Brian Kelly; Chiara Berardi; Ana Rita Sequeira; N. McGregor; A. Kellner; Shuli Brammli-Greenberg; Madeleine Hinwood; L. Murauskiene; Daiga Behmane; Zsolt J. Balogh; Terje P. Hagen; Francesco Paolucci. \textit{Social Science \& Medicine}, 2025. ``Are We Ready for the Next Pandemic? Public Preferences and Trade-offs between Vaccine Characteristics and Societal Restrictions across 21 Countries.'' \href{https://doi.org/10.1016/j.socscimed.2025.117687}{DOI: 10.1016/j.socscimed.2025.117687}
\item Mesfin Genie. \textit{Journal of Health Politics, Policy and Law}, 2025. ``Democracy, Trust, and Political Orientation: Disentangling Mechanisms Shaping Individuals’ Vaccine Attitudes.'' \href{https://doi.org/10.1215/03616878-12166725}{DOI: 10.1215/03616878-12166725}
\item Aregawi G. Gebremariam; Mesfin Genie; Huong Le; Katie Attwell; Bette Liu; Annette K. Regan; Frank H. Beard; Kristine Macartney; Francesco Paolucci; Hannah C. Moore; Christopher C. Blyth. \textit{BMJ Open}, 2025. ``Impact of Vaccine Mandates and Removals on COVID-19 Vaccine Uptake in Australia and International Comparators: A Study Protocol.'' \href{https://doi.org/10.1136/bmjopen-2024-097412}{DOI: 10.1136/bmjopen-2024-097412}
\item Tim C. Lai; Heather P. Whitley; Mesfin Genie; Robert H. Eckel; Surachat Ngorsuraches. \textit{Clinical Diabetes}, 2025. ``Important Continuous Glucose Monitoring Attributes for Patients with Type 2 Diabetes.'' \href{https://doi.org/10.2337/cd25-0047}{DOI: 10.2337/cd25-0047}
\item Martin J. Connor; Mesfin Genie; Tim Dudderidge; Hangjian Wu; Johanna Sukumar; Mark Beresford; Diletta Bianchini; C. Goh; G. Horan; P. Innominato; V. Khoo; N. Klimowska-Nassar; S. Madaan; S. Mangar; S. McCracken; P. Ostler; S. Paisey; A. Robinson; B. Rai; N. Sarwar; N. Srihari; K. T. Jayaprakash; M. Varughese; M. Winkler; Hashim U. Ahmed; Verity Watson. \textit{European Urology Oncology}, 2025. ``Patients’ Preferences for Cytoreductive Treatments in Newly Diagnosed Metastatic Prostate Cancer: The IP5-MATTER Study.'' \href{https://doi.org/10.1016/j.euo.2024.06.010}{DOI: 10.1016/j.euo.2024.06.010}
\item Fabio I. Martinenghi; Mesfin Genie; Katie Attwell; Huong Le; Hannah C. Moore; Aregawi G. Gebremariam; Bette Liu; Francesco Paolucci; Christopher C. Blyth. \textit{arXiv}, 2025. ``Vaccinating Now or Vaccinating Later: Separating Pull-Forward and Net Effects Using a Dynamic Regression Discontinuity Design.'' \href{https://doi.org/10.48550/arXiv.2509.22714}{DOI: 10.48550/arXiv.2509.22714}
\item Mesfin G. Genie; Nabin Poudel; Francesco Paolucci; Surachat Ngorsuraches. \textit{Value in Health}, 2024. ``Choice Consistency in Discrete Choice Experiments: Does Numeracy Skill Matter?.'' \href{https://doi.org/10.1016/j.jval.2024.07.001}{DOI: 10.1016/j.jval.2024.07.001}
\item Surachat Ngorsuraches; Mesfin Genie; Anna Solomon. \textit{American Journal of Pharmaceutical Education}, 2024. ``Doctor of Pharmacy Students’ Preferences for the Attributes of a Pharmacoeconomics Workshop: A Discrete Choice Experiment.'' \href{https://doi.org/10.1016/j.ajpe.2024.101089}{DOI: 10.1016/j.ajpe.2024.101089}
\item Pablo Arija Prieto; Marcello Antonini; Mehdi Ammi; Mesfin Genie; Francesco Paolucci. \textit{Health Policy}, 2024. ``Political Determinants of COVID-19 Restrictions and Vaccine Rollouts: The Case of Regional Elections in Italy and Spain.'' \href{https://doi.org/10.1016/j.healthpol.2024.105082}{DOI: 10.1016/j.healthpol.2024.105082}
\item Marcello Antonini; Mesfin G. Genie; Arthur E. Attema; Katie Attwell; Zsolt J. Balogh; Daiga Behmane; Chiara Berardi; Shuli Brammli-Greenberg; Andrew Greenland; Terje P. Hagen; Madeleine Hinwood; C. James; A. Kellner; Brian Kelly; L. Murauskiene; N. McGregor; Alessia Melegaro; N. Moy; Ana Rita Sequeira; R. Singh; Aleksandra Torbica; Jeremy K. Ward; D. Yang; Francesco Paolucci. \textit{Health Policy and Technology}, 2024. ``Public Preferences for Vaccination Campaigns in the COVID-19 Endemic Phase: Insights from the VaxPref Database.'' \href{https://doi.org/10.1016/j.hlpt.2024.100849}{DOI: 10.1016/j.hlpt.2024.100849}
\item Asmita P. Khatiwada; Mesfin G. Genie; Aregawi G. Gebremariam; Tim C. Lai; Nabin Poudel; Surachat Ngorsuraches. \textit{Health Policy and Technology}, 2024. ``Vaccination and Non-pharmaceutical Interventions during COVID-19: Impact on Health and Non-health Outcomes in the US.'' \href{https://doi.org/10.1016/j.hlpt.2023.100792}{DOI: 10.1016/j.hlpt.2023.100792}
\item Aregawi G. Gebremariam; D. Abegaz; H. Y. Nigus; T. L. Argaw; M. Gerbaba; Mesfin G. Genie; Francesco Paolucci. \textit{Health Policy and Technology}, 2024. ``Vaccine Uptake and Effectiveness: Why Some African Countries Performed Better than Others?.'' \href{https://doi.org/10.1016/j.hlpt.2023.100820}{DOI: 10.1016/j.hlpt.2023.100820}
\item Laura Wall; Samantha Bunzli; Elizabeth Nelson; L. Hawke; Mesfin Genie; Madeleine Hinwood; Danielle Lang; M. Dowsey; P. Clarke; P. Choong; Zsolt J. Balogh; L. Lohmander; Francesco Paolucci. \textit{The Bone \& Joint Journal}, 2024. ``Willingness to Participate in Placebo-Controlled Surgical Trials of the Knee.'' \href{https://doi.org/10.1302/0301-620X.106B12.BJJ-2023-1266.R2}{DOI: 10.1302/0301-620X.106B12.BJJ-2023-1266.R2}
\item Mesfin G. Genie; Mandy Ryan; Nicolas Krucien. \textit{Health Economics}, 2023. ``Keeping an Eye on Cost: What Can Eye Tracking Tell Us about Attention to Cost Information in Discrete Choice Experiments?.'' \href{https://doi.org/10.1002/hec.4658}{DOI: 10.1002/hec.4658}
\item Martin J. Connor; Mesfin G. Genie; David Burns; E. J. Bass; M. Gonzalez; N. Sarwar; A. Falconer; S. Mangar; T. Dudderidge; V. Khoo; M. Winkler; Hashim U. Ahmed; Verity Watson. \textit{European Urology Open Science}, 2022. ``A Systematic Review of Patients’ Values, Preferences, and Expectations for the Treatment of Metastatic Prostate Cancer.'' \href{https://doi.org/10.1016/j.euros.2021.10.003}{DOI: 10.1016/j.euros.2021.10.003}
\item Y. Sun; H. Li; Z. Andlib; Mesfin G. Genie. \textit{Renewable Energy}, 2022. ``How Do Renewable Energy and Urbanization Cause Carbon Emissions? Evidence from Advanced Panel Estimation Techniques.'' \href{https://doi.org/10.1016/j.renene.2021.12.112}{DOI: 10.1016/j.renene.2021.12.112}
\item Luis E. Loría-Rebolledo; Mandy Ryan; Verity Watson; Mesfin G. Genie; Ruben A. Sakowsky; Daniel Powell; Shantini Paranjothy. \textit{BMJ Open}, 2022. ``Public Acceptability of Non-pharmaceutical Interventions to Control a Pandemic in the UK: A Discrete Choice Experiment.'' \href{https://doi.org/10.1136/bmjopen-2021-054155}{DOI: 10.1136/bmjopen-2021-054155}
\item F. Chien; C.-C. Hsu; Z. Andlib; M. I. Shah; T. Ajaz; Mesfin G. Genie. \textit{Integrated Environmental Assessment and Management}, 2022. ``The Role of Solar Energy and Eco-innovation in Reducing Environmental Degradation in China: Evidence from a QARDL Approach.'' \href{https://doi.org/10.1002/ieam.4500}{DOI: 10.1002/ieam.4500}
\item Martin J. Connor; Mesfin G. Genie; Michael Gonzalez; N. Sarwar; K. T. Jayaprakash; G. Horan; F. Hosking-Jervis; N. Klimowska-Nassar; J. Sukumar; T. Pokrovska; D. Basak; A. Robinson; M. Beresford; B. Rai; S. Mangar; V. Khoo; T. Dudderidge; A. Falconer; M. Winkler; Verity Watson; Hashim U. Ahmed. \textit{BMJ Open}, 2021. ``Metastatic Prostate Cancer Men’s Attitudes towards Treatment of the Local Tumour and Metastasis Evaluative Research (IP5-MATTER): Protocol for a Prospective, Multicentre Discrete Choice Experiment Study.'' \href{https://doi.org/10.1136/bmjopen-2021-048996}{DOI: 10.1136/bmjopen-2021-048996}
\end{itemize}
\end{document}
